Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-22 paper/tex/sections/discussion.tex
add 2 new caveats

\subsection{Caveats}\label{sec:caveats}
\textit{Population synthesis limitations:} As with any study involving a population synthesis code, our results rely on uncertain stellar and binary physics and the use of approximate fitting formulae. COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars. Much of the underlying physics is uncertain, such as the common envelope evolution and mass transfer physics. We attempt to understand the importance of these assumptions by varying over many different physics assumptions.

@@

>>>>

\subsection{Caveats}\label{sec:caveats}
\textit{Binary fraction and other normalisation choices}: For the normalisation of the detection rate we conservatively chose to set the binary fraction of all stars to 50\%. The binary fraction is uncertain and not well constrained, though we know it is higher for more massive stars \citep[e.g.][]{Sana+2012}. However, the choice of the binary fraction has a strong effect on our results. Increasing it to 70\% and 100\% would increase our expected detection rates for every physics variation by 30\% and 67\% respectively. We assume that the mass ratio of secondary stars is uniformly distributed and this could also have strong effect on our results. We highlight the uncertainty in the normalisation to point out that the exact magnitude of the rates in each case could change drastically as our understanding shifts, however changes to this normalisation would affect every variation equally and so the trends across variations are more robust.

\textit{Population synthesis limitations:} As with any study involving a population synthesis code, our results rely on uncertain stellar and binary physics and the use of approximate fitting formulae. COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars. Much of the underlying physics is uncertain, such as the common envelope evolution and mass transfer physics. We attempt to understand the importance of these assumptions by varying over many different physics assumptions.

@@

\textit{Large progenitor masses:} Due to the high metallicity population within the Milky Way, many of the black holes that are formed in our sample come from progenitors with large initial masses. 39\% of BHBHs contain a BH with a progenitor mass in excess of $100 \unit{M_\odot}$, as do $13\%$ of BHNSs. The fitting formulae upon with COMPAS is based need to be extrapolated for stars of this mass and so their true evolution may not follow the results of population synthesis.
